### 2023-06-22 manuscript.tex
Merge branch 'main' of github.com:stain/2022-fdo-paper into main [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/6d9233550171f4d9f517b3a485faa60d68c64d34.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/6d9233550171f4d9f517b3a485faa60d68c64d34/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5340366129

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/6f7e00b05e91c1799cc3ea6c819f517ab11786ee/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/6f7e00b05e91c1799cc3ea6c819f517ab11786ee}{stain/2022-fdo-paper@6f7e00b}
on June 19, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-1BlxdxOwa}{}}%
14:00-17:00.ISO 16684-1:2019. \emph{Available at} \href{https://www.iso.org/standard/75163.html}{\emph{https://www.iso.org/standard/75163.html}} (accessed 19 June 2023b).

@@

\leavevmode\vadjust pre{\hypertarget{ref-11dInoyVF}{}}%
5-star Open Data. \emph{Available at} \href{http://5stardata.info/en/}{\emph{http://5stardata.info/en/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-zt8AAjcZ}{}}%
Data Catalog Vocabulary (DCAT) - Version 2. \emph{Available at} \href{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}{\emph{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}} (accessed 19 June 2023b).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1EW4hLN8U}{}}%
Data Catalog Vocabulary (DCAT) - Version 3. \emph{Available at} \href{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}{\emph{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}} (accessed 19 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-6LvydTsC}{}}%
Data Information View. \emph{Available at} \href{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}{\emph{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}} (accessed 19 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-hKblceo6}{}}%
DCMI Metadata Terms. 2020. \emph{Available at} \href{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}{\emph{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-68fzID2k}{}}%
DOI® Handbook. \emph{Available at} \href{https://www.doi.org/the-identifier/resources/handbook/}{\emph{https://www.doi.org/the-identifier/resources/handbook/}} (accessed 19 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-1H9iQhQYq}{}}%
DOI® Resolution Documentation. \emph{Available at} \href{https://www.doi.org/the-identifier/resources/factsheets/doi-resolution-documentation}{\emph{https://www.doi.org/the-identifier/resources/factsheets/doi-resolution-documentation}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-p7nwRj8E}{}}%
DOIP API for HTTP Clients --- Cordra documentation. \emph{Available at} \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{\emph{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CvYRVhy2}{}}%
Handle.Net Registry. \emph{Available at} \href{https://www.handle.net/download_hnr.html}{\emph{https://www.handle.net/download\_hnr.html}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-13PaKBrZe}{}}%
Hydra W3C Community Group. \emph{Available at} \href{https://www.hydra-cg.com/}{\emph{https://www.hydra-cg.com/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-nW4HY8Nq}{}}%
"info" URI Registry (Frozen). \emph{Available at} \href{https://oclc-research.github.io/infoURI-Frozen/}{\emph{https://oclc-research.github.io/infoURI-Frozen/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-xVJMmGVr}{}}%
Licenses. 2022. \emph{Available at} \href{https://opensource.org/licenses/}{\emph{https://opensource.org/licenses/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-QpDmajc4}{}}%
Linking Across Provenance Bundles. \emph{Available at} \href{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}{\emph{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-i9Ang0rM}{}}%
martinekuan. 2023.Web API design best practices - Azure Architecture Center. \emph{Available at} \href{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}{\emph{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-ID1pTGry}{}}%
ORE Specification - Abstract Data Model. \emph{Available at} \href{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}{\emph{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}} (accessed 19 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-gtGuSevK}{}}%
ORE User Guide - Primer. \emph{Available at} \href{http://www.openarchives.org/ore/1.0/primer}{\emph{http://www.openarchives.org/ore/1.0/primer}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-9T4j3N4e}{}}%
PROV-O: The PROV Ontology. \emph{Available at} \href{https://www.w3.org/TR/2013/REC-prov-o-20130430/}{\emph{https://www.w3.org/TR/2013/REC-prov-o-20130430/}} (accessed 19 June 2023a).

\leavevmode\vadjust pre{\hypertarget{ref-ZUgwvAHE}{}}%
PROV-O: The PROV Ontology. \emph{Available at} \href{https://www.w3.org/TR/prov-o/\#specializationOf}{\emph{https://www.w3.org/TR/prov-o/\#specializationOf}} (accessed 19 June 2023b).

@@

\leavevmode\vadjust pre{\hypertarget{ref-voDQ6diM}{}}%
The ARK Identifier Scheme. \emph{Available at} \href{https://datatracker.ietf.org/doc/id/draft-kunze-ark.html}{\emph{https://datatracker.ietf.org/doc/id/draft-kunze-ark.html}} (accessed 19 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-hxtgCGjY}{}}%
The Modern Standards Paradigm - Five Key Principles. \emph{Available at} \href{https://open-stand.org/about-us/principles/}{\emph{https://open-stand.org/about-us/principles/}} (accessed 19 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-10HA0mMBx}{}}%
Unknown.Introducing 'Role'. \emph{Available at} \href{http://blog.schema.org/2014/06/introducing-role.html}{\emph{http://blog.schema.org/2014/06/introducing-role.html}} (accessed 19 June 2023).

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/6d9233550171f4d9f517b3a485faa60d68c64d34/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/6d9233550171f4d9f517b3a485faa60d68c64d34}{stain/2022-fdo-paper@6d92335}
on June 22, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-1BlxdxOwa}{}}%
14:00-17:00.ISO 16684-1:2019. \emph{Available at} \href{https://www.iso.org/standard/75163.html}{\emph{https://www.iso.org/standard/75163.html}} (accessed 21 June 2023b).

@@

\leavevmode\vadjust pre{\hypertarget{ref-11dInoyVF}{}}%
5-star Open Data. \emph{Available at} \href{http://5stardata.info/en/}{\emph{http://5stardata.info/en/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-zt8AAjcZ}{}}%
Data Catalog Vocabulary (DCAT) - Version 2. \emph{Available at} \href{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}{\emph{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}} (accessed 21 June 2023b).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1EW4hLN8U}{}}%
Data Catalog Vocabulary (DCAT) - Version 3. \emph{Available at} \href{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}{\emph{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}} (accessed 21 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-6LvydTsC}{}}%
Data Information View. \emph{Available at} \href{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}{\emph{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}} (accessed 21 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-hKblceo6}{}}%
DCMI Metadata Terms. 2020. \emph{Available at} \href{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}{\emph{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-68fzID2k}{}}%
DOI® Handbook. \emph{Available at} \href{https://www.doi.org/the-identifier/resources/handbook/}{\emph{https://www.doi.org/the-identifier/resources/handbook/}} (accessed 21 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-1H9iQhQYq}{}}%
DOI® Resolution Documentation. \emph{Available at} \href{https://www.doi.org/the-identifier/resources/factsheets/doi-resolution-documentation}{\emph{https://www.doi.org/the-identifier/resources/factsheets/doi-resolution-documentation}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-p7nwRj8E}{}}%
DOIP API for HTTP Clients --- Cordra documentation. \emph{Available at} \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{\emph{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CvYRVhy2}{}}%
Handle.Net Registry. \emph{Available at} \href{https://www.handle.net/download_hnr.html}{\emph{https://www.handle.net/download\_hnr.html}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-13PaKBrZe}{}}%
Hydra W3C Community Group. \emph{Available at} \href{https://www.hydra-cg.com/}{\emph{https://www.hydra-cg.com/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-nW4HY8Nq}{}}%
"info" URI Registry (Frozen). \emph{Available at} \href{https://oclc-research.github.io/infoURI-Frozen/}{\emph{https://oclc-research.github.io/infoURI-Frozen/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-xVJMmGVr}{}}%
Licenses. 2022. \emph{Available at} \href{https://opensource.org/licenses/}{\emph{https://opensource.org/licenses/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-QpDmajc4}{}}%
Linking Across Provenance Bundles. \emph{Available at} \href{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}{\emph{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-i9Ang0rM}{}}%
martinekuan. 2023.Web API design best practices - Azure Architecture Center. \emph{Available at} \href{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}{\emph{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-ID1pTGry}{}}%
ORE Specification - Abstract Data Model. \emph{Available at} \href{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}{\emph{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}} (accessed 21 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-gtGuSevK}{}}%
ORE User Guide - Primer. \emph{Available at} \href{http://www.openarchives.org/ore/1.0/primer}{\emph{http://www.openarchives.org/ore/1.0/primer}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-9T4j3N4e}{}}%
PROV-O: The PROV Ontology. \emph{Available at} \href{https://www.w3.org/TR/2013/REC-prov-o-20130430/}{\emph{https://www.w3.org/TR/2013/REC-prov-o-20130430/}} (accessed 21 June 2023a).

\leavevmode\vadjust pre{\hypertarget{ref-ZUgwvAHE}{}}%
PROV-O: The PROV Ontology. \emph{Available at} \href{https://www.w3.org/TR/prov-o/\#specializationOf}{\emph{https://www.w3.org/TR/prov-o/\#specializationOf}} (accessed 21 June 2023b).

@@

\leavevmode\vadjust pre{\hypertarget{ref-voDQ6diM}{}}%
The ARK Identifier Scheme. \emph{Available at} \href{https://datatracker.ietf.org/doc/id/draft-kunze-ark.html}{\emph{https://datatracker.ietf.org/doc/id/draft-kunze-ark.html}} (accessed 21 June 2023).

\leavevmode\vadjust pre{\hypertarget{ref-hxtgCGjY}{}}%
The Modern Standards Paradigm - Five Key Principles. \emph{Available at} \href{https://open-stand.org/about-us/principles/}{\emph{https://open-stand.org/about-us/principles/}} (accessed 21 June 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-10HA0mMBx}{}}%
Unknown.Introducing 'Role'. \emph{Available at} \href{http://blog.schema.org/2014/06/introducing-role.html}{\emph{http://blog.schema.org/2014/06/introducing-role.html}} (accessed 21 June 2023).
